Title

### 2023-09-06 paper/paper.tex
paper

\subsection{Single amminoacid contextual representation}
We tried four methods to join togheter the amminoacid embeddings in order to produce a fixed size embedding for the chunk: average, maximum, sum and principal component analysis (PCA). Note that even if these operators are commutative, the overall process do takes into account the order of the amminoacids precisely because the embeddings are contextual.

@@

>>>>

\subsection{Combining the contextual representations}
We tried four methods to join togheter the amminoacid embeddings in order to produce a fixed size embedding for the chunk: average, maximum, sum and principal component analysis (PCA). Note that even if these operators are commutative, the overall process do takes into account the order of the amminoacids precisely because the embeddings are contextual.

@@

\subsection{Comparison with known informations}
Given a set of embeddings of sequences we want to analyze their distribution in the embedding space comparing it with both the distance matrix produced during the multiple sequence alignment with Clustal Omega \cite{sievers2011fast} and protein annotations as gene ontology, UniProt keywords and taxonimy \cite{uniprot23}.

\subsubsection{Allignment distance}
In order to compare the distances between the sequences in the embedding space with the alignment distance we performed an agglomerative clustering on both the matrices, the resulting tree is then cut at each levels: flat partitions of all possibles number of clusters are produced. We perform a comparison of the partitions with the same number of clusters using the adjusted rand score \cite{hubert1985comparing}. The mean of these score, starting from two clusters up to $ \#elements - 1 $ clusters is called mean adjusted rand score (MARS).
